\documentclass[11pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[default]{lato}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{ragged2e}
\usepackage{fontawesome}
\usepackage{enumitem}
\DeclareFontFamily{U}{fontawesomeOne}{}
\DeclareFontShape{U}{fontawesomeOne}{m}{n}
{<-> FontAwesome--fontawesomeone}{}
\DeclareRobustCommand\FAone{\fontencoding{U}\fontfamily{fontawesomeOne}\selectfont}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
{\setlength{\leftmargin}{#1}}%
     \item[]
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
{\setlength{\leftmargin}{-0.5#1}}%
\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
#1 &
#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
    {\LARGE \textbf{Nguyen Phu Quang}}\\
    Ho Chi Minh, Vietnam
    \vspace{0.1cm}
    \\
    \raisebox{-0.2\height} {\Large \faPhoneSquare} \ \  +84 913501314 \hfill quangnguyen16200@gmail.com \ \ \raisebox{-0.2\height}{\Large \faEnvelopeSquare}
    \\
    \raisebox{-0.2\height}{\Large \faGithubSquare} \ \ github.com/McPepperoni \hfill linkedin.com/in/quang-nguyen-549926212 \raisebox{-0.2\height}{\Large \faLinkedinSquare}
\end{center}

\hrule
\vspace{.5cm}
\justifying
I'm a software engineer who are eager to learn and understand technology. Begin as Computer Sciences student ignites my passion to work with creating software to better life. I have deep understand on multiple technology
from Front-end to Back-end to Mobile.
\vspace{.5cm}

\hrule
\vspace{-1em}
\subsection*{\Large Experience}

\renewcommand\labelitemi{}
\renewcommand\labelitemii{$\bullet$}
\begin{itemize}[leftmargin=1em]
    \parskip=0.1em


    \item
          \headerrow
          {\textbf{Renesas Design Vietnam}}
          {\textbf{Tan Thuan, District 7, Ho Chi Minh}}
          \headerrow
          {\emph{Software Engineer}}
          {\emph{July 2023 -- Present}}
          {\emph{Java/Springboot - ReactJS/NextJS/TS - Python/SQL - OracleDB/PostgreSQL}}

          \begin{itemize*}
              \item Analyzing and working out data oriented softwares solution to aid company production processes. Building \textbf{APIs, Data Wranglers, User Interfaces,\dots}
              \item Maintaining and renovating legacy softwares.
              \item Deloying, test and setting up \textbf{Linux} environments.
              \item Leading \textbf{small teams} of developer.
              \item Working with \textbf{Agile PLM} databases, optimized software solution for over \textbf{1.000.000 lines} of data. Clean up data/extracting reports for business needs.
              \item Building database specific extensions.
              \item Using \textbf{Java/Springboot} for \textbf{backend} and \textbf{React/NextJS} for \textbf{frontend}.
              \item Building and scaling microservices from scratch and setup tools to aid development/optimization process like \textbf{Elk Stack} for log management, \textbf{Oracle database}, \textbf{Kafka} to further optimized software.
              \item Writing and optimizing \textbf{Docker} files for services.
              \item Implementing apllication security with \textbf{Keycloak/Spring Security/OIDC}.
          \end{itemize*}

    \item
          \headerrow
          {\textbf{Freelance Software Engineer}}
          {\textbf{}}
          \headerrow
          {\emph{NextJS - Java - NodeJS - Python - Docker - PostgreSQL/Firebase/SQL}}
          {\emph{November 2022 - Present}}
          \begin{itemize*}
              \item Advice, giving out solutions and building application for users needs.
              \item Deploying, testing application using \textbf{Docker} on \textbf{Linux} servers.
              \item Working on multiple type of application from \textbf{webapps} to \textbf{scriptings}.
          \end{itemize*}

    \item
          \headerrow
          {\textbf{Success Software Services}}
          {\textbf{Ward 12, Tan Binh District, Ho Chi Minh}}
          \headerrow
          {\emph{Fresher Backend Software Engineer}}
          {\emph{January 2023 - July 2023}}
          {\emph{C\#/.Net}}
          \begin{itemize*}
              \item Implementing designs and requirements for large scale ecommerce application.
              \item Maintaining, renovating legacy softwares.
              \item Participate in meeting comunicating with end users to advice solutions best fit requirements.
              \item Aids in DevOPs process by building and optimizing \textbf{Docker} files
          \end{itemize*}
          \headerrow
          {\emph{Intern Backend Software Engineer}}
          {\emph{November 2022 - January 2023}}
          \begin{itemize*}
              \item Participate in training sessions on \textbf{C\#, .Net}.
              \item Building from scratch ecommerce projects.
          \end{itemize*}

    \item
          \headerrow
          {\textbf{Vitalify Asia}}
          {\textbf{Vo Thi Sau Ward, District 3, Ho Chi Minh}}
          \headerrow
          {\emph{Fresher Frontend Software Engineer}}
          {\emph{August 2022 - November 2022}}
          {\emph{ReactJS/TS}}
          \begin{itemize*}
              \item Developed internals ERP tools.
              \item Working with designers and customers to improve user interfaces.
          \end{itemize*}

\end{itemize}

\hrule
\vspace{-1em}
\subsection*{\Large Skills}

\hyphenpenalty=1000
\begin{itemize}[leftmargin=1em,noitemsep]
    \item \textbf{Technologies:}
          Java, C\#, HTML/CSS, Typescripts, \LaTeX, Python, SQL, Docker
    \item \textbf{Software:}
          Atlassian (Bitbucket, Jira, Confluence), Oracle System (Red Hat Linux, Agile PLM Systems, OracleDB)
\end{itemize}

\hrule
\vspace{-1em}
\subsection*{\Large Education}

\begin{itemize}[leftmargin=1em]
    \parskip=0.1em

    \item
          \headerrow
          {\textbf{University of Information and Technologies}}
          {\textbf{HCM VNU, Ho Chi Minh}}
          \headerrow
          {\emph{B.S. Computer Science} (\textbf{GPA:} 7.54/10)}
          {\emph{September 2019 -- May 2024}}


\end{itemize}

\end{document}