\documentclass[11pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[default]{lato}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{ragged2e}
\usepackage{fontawesome}
\usepackage{enumitem}
\DeclareFontFamily{U}{fontawesomeOne}{}
\DeclareFontShape{U}{fontawesomeOne}{m}{n}
{<-> FontAwesome--fontawesomeone}{}
\DeclareRobustCommand\FAone{\fontencoding{U}\fontfamily{fontawesomeOne}\selectfont}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
{\setlength{\leftmargin}{#1}}%
     \item[]
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
{\setlength{\leftmargin}{-0.5#1}}%
\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
#1 &
#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
    {\LARGE \textbf{Nguyen Phu Quang}}\\
    \vspace{0.2cm}
    Software Engineer\\
    \vspace{0.2cm}
    Ho Chi Minh, Vietnam
    \vspace{0.5cm}
    \\
    \raisebox{-0.2\height} {\Large \faPhoneSquare} \ \  +84 913501314 \hfill quangnguyen16200@gmail.com \ \ \raisebox{-0.2\height}{\Large \faEnvelopeSquare}
    \\
    \raisebox{-0.2\height}{\Large \faGithubSquare} \ \ github.com/McPepperoni \hfill linkedin.com/in/quang-nguyen-549926212 \raisebox{-0.2\height}{\Large \faLinkedinSquare}
\end{center}

\hrule
\vspace{.5cm}
\justifying
I'm a software engineer who are eager to learn and understand technology. Begin as Computer Sciences student ignites my passion to work with creating software to better life. I have deep understand on multiple technology
from Front-end to Back-end to Mobile.
\vspace{.5cm}

\hrule
\vspace{-1em}
\subsection*{\Large Experience}

\renewcommand\labelitemi{}
\renewcommand\labelitemii{$\bullet$}
\begin{itemize}[leftmargin=1em]
    \parskip=0.1em


    \item
          \headerrow
          {\large\textbf{Renesas Design Vietnam}}
          {\textbf{Tan Thuan, District 7, Ho Chi Minh}}
          \headerrow
          {\emph{Software Engineer}}
          {\emph{July 2023 -- Present}}
          {\emph{Java/Springboot - ReactJS/NextJS/TS - Python/SQL - OracleDB/PostgreSQL}}\\

          \textbf{Extracting} and \textbf{wrangling} data from AgilePLM.
          \textbf`'{Building microservices based application} PLM supporting applications.
          \begin{enumerate}
              \item
                    \headerrow
                    {\textbf{PLM APART - License administrative monitoring portal}}
                    {\emph{}}
                    {\emph{Java springboot - NextJS - AgilePLM}}

                    \begin{itemize*}
                        \item Building \textbf{Apis} and \textbf{User interface} for \textbf{Readonly metrics} of license usages.
                        \item Tracking license/user changes.
                        \item Building chart components for statistics.
                    \end{itemize*}
              \item
                    \headerrow
                    {\textbf{PLM AUDIT - User auditing system}}
                    {\emph{}}
                    {\emph{Java springboot - NextJS - Kafka - AgilePLM - Postgres - Docker - Camunda}}

                    \begin{itemize*}
                        \item Building \textbf{Apis} and \textbf{User interface} for \textbf{Scheduled RBAC} based application for administrative board to monitor and audit \textbf{System licenses} and \textbf{Account usages}.
                        \item Integrating with \textbf{Kafka} and \textbf{Camunda} for managing running business processes.
                        \item Implementing RBAC on NextJS application based on required design. Optimized user experience with \textbf{SSR.}
                        \item \textbf{Response to feedback, monitoring, testing} and supporting end users.
                    \end{itemize*}
              \item
                    \headerrow
                    {\textbf{FIESTA - Data migration}}
                    {\emph{}}
                    {\emph{Java springboot - Kafka - AgilePLM - OracleDB - Docker}}

                    \begin{itemize*}
                        \item Implementing and building \textbf{APIs, Data Wranglers,\dots} migrating data from PLM System to to others.
                        \item Brain storming and reacting to requirements change and implementing \textbf{scalable system} with \textbf{Kafka} and \item{Master/Worker} to handle giant loads of data and ensuring service uptime.
                        \item Support development by \textbf{deploying relevant tools} to development environment using \textbf{Docker}.
                    \end{itemize*}
              \item
                    \headerrow
                    {\textbf{ARET - Report portal}}
                    {\emph{}}
                    {\emph{Java springboot - NextJS - AgilePLM}}

                    \begin{itemize*}
                        \item Implementing and building \textbf{APIs, Data Wranglers, User Interfaces,\dots} for relevant employees to access reports of certain manufacturing processes.
                        \item Referencing old implementation to renovate and implement on Microservices structures.\\
                    \end{itemize*}
          \end{enumerate}

    \item
          \headerrow
          {\large\textbf{Freelance Software Engineer}}
          {\textbf{}}
          \headerrow
          {\emph{NextJS - Java - NodeJS - Python - Docker - PostgreSQL/Firebase/SQL}}
          {\emph{November 2022 - Present}}
          \begin{enumerate}
              \item
                    \headerrow
                    {\textbf{CodeZX - Longchass}}
                    {\emph{}}
                    {\emph{Java springboot - NextJS - Postgres - Google Cloud - AWS - CI/CD - Vercel - Jenkins - Docker - Kafka - Kong Api Gateway}}

                    \begin{itemize*}
                        \item Building \textbf{all in one} \textbf{Landing Page} and \textbf{CMS/CRM} application for client outreach and deal managements.
                        \item \textbf{Optimizing SEO} and \textbf{SSR} for performances and accessibility.
                        \item Integrate with Google for \textbf{Authentication/Email managements/Business metrics} including client/leads managements.
                        \item Setup AWS environment for deployment with Docker.
                        \item Building CICD pipeline for deployment with Jenkins.
                    \end{itemize*}
              \item
                    \headerrow
                    {\textbf{CodeZX - Coffeeshop}}
                    {\emph{}}
                    {\emph{Java springboot - NextJS - Flutter - Postgres - Kafka - Google Cloud - CI/CD - Vercel - Jenkins - Docker - Kafka - Kong Api Gateway}}

                    \begin{itemize*}
                        \item Building \textbf{Apis} and \textbf{User interface} for \textbf{contactless ordering} on or off-store including promotion campaigns and advertisements.
                        \item Integrating online payment methods like \textbf{Momo/VietQr}.
                        \item \textbf{Tracking order} and building \textbf{notification system} with \textbf{Kafka}.
                        \item Building mobile version of application using Flutter for accessibility.
                        \item Building email notification system.
                        \item Setup \textbf{Jenkins for CICD} and \textbf{Kong for Routing};
                        \item Working with \textbf{DNS} for \textbf{Mapping domains} and \textbf{config SSL}.
                    \end{itemize*}
              \item
                    \headerrow
                    {\textbf{Supplement ecommerce portal}}
                    {\emph{}}
                    {\emph{NodeJS - NextJS - Postgres - Firebase - Google Cloud - CI/CD - Vercel - Jenkins - Docker}}

                    \begin{itemize*}
                        \item Building \textbf{Apis} and \textbf{User interface} for \textbf{Healthcare Supplements}.
                        \item Integrating online payment methods like \textbf{Momo/VietQr}.
                        \item \textbf{Tracking order} and building \textbf{notification system} with \textbf{Firebase}.
                        \item Working with \textbf{DNS} for \textbf{Mapping domains} and \textbf{config SSL}.\\
                    \end{itemize*}
          \end{enumerate}

    \item
          \headerrow
          {\large\textbf{Success Software Services}}
          {\textbf{Ward 12, Tan Binh District, Ho Chi Minh}}
          \headerrow
          {\emph{Fresher Backend Software Engineer}}
          {\emph{January 2023 - July 2023}}
          {\emph{C\#/.Net}}
          \begin{itemize*}
              \item Implementing designs and requirements for large scale ecommerce application.
              \item Maintaining, renovating legacy softwares.
              \item Participate in meeting comunicating with end users to advice solutions best fit requirements.
              \item Aids in DevOPs process by building and optimizing \textbf{Docker} files
          \end{itemize*}
          \headerrow
          {\emph{Intern Backend Software Engineer}}
          {\emph{November 2022 - January 2023}}
          \begin{itemize*}
              \item Participate in training sessions on \textbf{C\#, .Net}.
              \item Building from scratch ecommerce projects.
          \end{itemize*}

    \item
          \headerrow
          {\large\textbf{Vitalify Asia}}
          {\textbf{Vo Thi Sau Ward, District 3, Ho Chi Minh}}
          \headerrow
          {\emph{Fresher Frontend Software Engineer}}
          {\emph{August 2022 - November 2022}}
          {\emph{ReactJS/TS}}
          \begin{itemize*}
              \item Developed internals ERP tools.
              \item Working with designers and customers to improve user interfaces.\\
          \end{itemize*}

\end{itemize}

\hrule
\vspace{-1em}
\subsection*{\Large Skills}

\hyphenpenalty=1000
\begin{itemize}[leftmargin=1em,noitemsep]
    \item \textbf{Technologies:}
          Java, C\#, HTML/CSS, Typescripts, \LaTeX, Python, SQL, Docker
    \item \textbf{Software:}
          Atlassian (Bitbucket, Jira, Confluence), Oracle System (Red Hat Linux, Agile PLM Systems, OracleDB)
\end{itemize}

\hrule
\vspace{-1em}
\subsection*{\Large Education}

\begin{itemize}[leftmargin=1em]
    \parskip=0.1em

    \item
          \headerrow
          {\textbf{University of Information and Technologies}}
          {\textbf{HCM VNU, Ho Chi Minh}}
          \headerrow
          {\emph{B.S. Computer Science} (\textbf{GPA:} 7.54/10)}
          {\emph{September 2019 -- May 2024}}


\end{itemize}

\end{document}